---
title: "Moby Dick - Ordered"
format:
 html:
  mainfont: Newsreader
  theme:
   - styles.scss
---

::: {.panel-tabset} 

## Book

Every sentence is its own row. Click "ABC Order" or another column header to sort sentences in a new order. Click it again for descending. Clicking "Original Order" will reset everything.  

::: {.callout-tip title="Why?" collapse="true"}
Dwight Garner of The New York Times and Becca Rothfeld of The Washington Post discussed their 2024 book reviews with Kara Swisher on [an episode of Kara's podcast, On with Kara Swisher](https://podcasts.apple.com/us/podcast/the-best-and-most-overrated-books-of-2024/id1643307527?i=1000681397924).

Dwight noted that reading sentences out of context lets you focus on the writer's skill at the level of sentences. 
:::

```{r}
#| include: false
library(reactable)
```


```{r}
#| include: false
text <- readRDS("data/text-clean.Rds")
```


```{r}
#| echo: false
#| column: page

text |> 
    reactable(
        searchable = FALSE,
        filterable = FALSE,
        pagination = FALSE,
        defaultSorted = "order_original",
        columns = list(
            text = colDef(
                name = "Sentence",
                class = "medium",
                minWidth = 300,
                maxWidth = 650
            ),
            order_original = colDef(
                name = "Original Order",
                class = "smol",
                maxWidth = 100
            ),
            order_n_characters = colDef(
                name = "Number of Characters",
                class = "smol",
                maxWidth = 150,
                minWidth = 100,
            ),
            order_abc = colDef(
                name = "ABC Order",
                class = "smol",
                maxWidth = 100
            )
        ),
        columnGroups = list(
          colGroup(name = "Sort with these columns",
          columns = c("order_original", "order_abc", "order_n_characters"))
        ),
        theme = reactableTheme(
            backgroundColor = "#f2e9df",
            borderColor = "#f2e9df",
            headerStyle = list(backgroundColor = "#e5d8cb"),

        )
    )
```

## About

<br>

This page was created by [Jeremy Allen](https://bsky.app/profile/jeremy-data.bsky.social). [The code is available here](https://github.com/jeremy-allen/ascending_books). John Harmon's *[gutenbergr](https://docs.ropensci.org/gutenbergr/)* R package was used to retrieve the text from [Project Gutenberg](https://www.gutenberg.org/). Text processing was done with *[tidyverse](https://www.tidyverse.org/)* packages and the *[tidytext](https://juliasilge.github.io/tidytext/)* package by Julia Silge and David Robinson. This page was built with Posit's [Quarto](https://quarto.org/) framework and *[reactable](https://glin.github.io/reactable/index.html)* package. This page is hosted on a [Posit Connect](https://posit.co/products/enterprise/connect/) server.

**Project Gutenberg book information:**

The Project Gutenberg eBook of Moby-Dick; or, The Whale
    
This ebook is for the use of anyone anywhere in the United States and
most other parts of the world at no cost and with almost no restrictions
whatsoever. You may copy it, give it away or re-use it under the terms
of the Project Gutenberg License included with this ebook or online
at www.gutenberg.org. If you are not located in the United States,
you will have to check the laws of the country where you are located
before using this eBook.

Title: Moby-Dick; or, The Whale

Author: Herman Melville

Release date: May 1, 1991 [eBook #15]
                Most recently updated: March 6, 2024

Language: English

Credits: Eugene F. Irey

### References

Harmon J, Johnston M, Bradford J, Robinson D (2024). *gutenbergr: Download and Process Public Domain Works from Project Gutenberg.* R package version 0.2.4.9000, [https://github.com/ropensci/gutenbergr](https://github.com/ropensci/gutenbergr), [https://docs.ropensci.org/gutenbergr/](https://docs.ropensci.org/gutenbergr/).  

Lin G (2024). *reactable: Interactive Data Tables for R*. R package version 0.4.4.9000, https://github.com/glin/reactable, [https://glin.github.io/reactable/](https://glin.github.io/reactable/).  

Silge J, Robinson D (2016). “tidytext: Text Mining and Analysis Using Tidy Data Principles in R.” *JOSS*, 1(3). doi:10.21105/joss.00037, [http://dx.doi.org/10.21105/joss.00037](https://doi.org/10.21105/joss.00037).

Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry L, Hester J, Kuhn M, Pedersen TL, Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel DP, Spinu V, Takahashi K, Vaughan D, Wilke C, Woo K, Yutani H (2019). “Welcome to the tidyverse.” *Journal of Open Source Software*, 4(43), 1686. [doi:10.21105/joss.01686](https://doi.org/10.21105/joss.01686).  

:::
